Soss

### 2020-01-02 paper/paper.tex
edits

In the above, a \emph{distribution} refers to a joint distribution, while \emph{point} refers to a named tuple in the space space of a given distribution.

@@

@@

\todo[inline]{Cite SimplePosets and SimpleGraphs}

>>>>

In the above, a \emph{distribution} refers to a joint distribution, while \emph{point} refers to a named tuple in the space space of a distribution.

@@

\subsection{Inference}

\jl#DynamicHMC.jl# \cite{tamas_k_papp_2019_3590018}

@@

Soss represents and manipulates variable dependencies using \jl#SimpleGraphs#, \jl#SimplePosets#, and \jl#SimplePartitions# from \cite{SimpleWorld}.
